The development of children's ability to track and predict turn structure in conversation

### 2015-11-28 paper/CasillasFrank-Anticip.tex
some additions to the general discussion, not yet complete

\usepackage{graphicx}
% \usepackage{lineno}
\usepackage{amssymb}
\usepackage{wrapfig}
\usepackage{subfig}
\usepackage{tipa}
\usepackage{float}

@@

\begin{table}[h!]
\begin{center}
  \begin{tabular}{lcccl}
  \textbf{\textit{Children}} &&&& \\
    \hline
                       & Estimate & Std. Error & z value & Pr($>$$|$z$|$)    \\
    \hline
    (Intercept)                & -3.57414  &   0.48576 &  -7.358 & 1.87e-13 ***    \\
    Age                         & 0.02543 &    0.10260  &  0.248   & 0.8042        \\
    Condition$=$\textit{muffled}         &   -1.63429  &   0.86390 &  -1.892   & 0.0585 .      \\
    Condition$=$\textit{normal}            &  0.36710 &    0.43296 &   0.848  &  0.3965        \\
    Condition$=$\textit{robot}            &  -0.26741 &    0.59071 &  -0.453  &  0.6508        \\
    Type$=$\textit{non-Question}                      & -0.81873  &   0.59985 &  -1.365  &  0.1723        \\
    Duration                   &  4.17672  &   0.62446  &  6.689 & 2.25e-11 ***    \\
    Age*Condition$=$\textit{muffled}       &   0.39317 &     0.18907 &   2.080  &  0.0376 *      \\
    Age*Condition$=$\textit{normal}       &   0.12919 &    0.10227  &  1.263  &  0.2065        \\
    Age*Condition$=$\textit{robot}           &   0.13740  &   0.13568   & 1.013  &  0.3112        \\
    Age*Type$=$\textit{non-Question}                &    0.15116   &  0.13643  &  1.108  &  0.2679        \\
    Condition$=$\textit{muffled}*     &  1.77190  &   1.24864  &  1.419 &   0.1559        \\
    Type$=$\textit{non-Question} &&&& \\
    Condition$=$\textit{normal}*     &   0.91059  &   0.72095  &  1.263 &   0.2066        \\
    Type$=$\textit{non-Question} &&&& \\
    Condition$=$\textit{robot}*     &   -1.02193  &   1.01227  & -1.010  &  0.3127        \\
    Type$=$\textit{non-Question} &&&& \\
    Age*Condition$=$\textit{muffled}* &  -0.47057 &    0.28703 &  -1.639 &   0.1011        \\
    Type$=$\textit{non-Question} &&&& \\
    Age*Condition$=$\textit{normal}* &   -0.37542  &   0.16963  & -2.213 &   0.0269 *      \\
    Type$=$\textit{non-Question} &&&& \\
    Age*Condition$=$\textit{robot}*  &   0.08946  &   0.22349   & 0.400 &   0.6890        \\
    Type$=$\textit{non-Question} &&&& \\
    \hline
  &&&& \\
  \textbf{\textit{Adults}} &&&& \\
    \hline
                       &  Estimate & Std. Error & z value & Pr($>$$|$z$|$) \\    
    \hline
    (Intercept)           &  -3.4557   &   0.7199 &  -4.800 & 1.58e-06 *** \\ 
    Condition$=$\textit{muffled}     &     0.3349  &    0.8965  &  0.374 & 0.708692     \\ 
    Condition$=$\textit{normal}    &      1.2556   &   0.5633  &  2.229 & 0.025805 *   \\ 
    Condition$=$\textit{robot}       &     1.5938  &    0.7208 &   2.211 & 0.027023 *   \\ 
    Type$=$\textit{non-Question}                  &   0.4292  &    0.6089  &  0.705 & 0.480916     \\ 
    Duration             &     4.7500   &   1.2480  &  3.806 & 0.000141 *** \\ 
    Condition$=$\textit{muffled}*  &  0.6627  &    1.2138 &   0.546 & 0.585108     \\ 
    Type$=$\textit{non-Question} &&&& \\
    Condition$=$\textit{normal}* &   -0.9452  &    0.7631 &  -1.239 & 0.215475     \\ 
    Type$=$\textit{non-Question} &&&& \\
    Condition$=$\textit{robot}*   &  -1.1265  &    0.9109  & -1.237 & 0.216201     \\ 
    Type$=$\textit{non-Question} &&&& \\
    \hline
  \end{tabular}
\end{center}
  \caption{Model output for children and adults' anticipatory gaze switches.}
\label{tab:E2-models}
\end{table}

@@

@@

% CAN USE LATER: Because the form of an answer is partially determined by its question (e.g., locative expressions for ``where'' questions), participants could even be predicting what type of response they will hear, and so they are looking anticipatorily at the responder for confirmation of their prediction. This interpretation is initial, but in-line with work showing early response planning and speech act recognition \citep{gisladottir2015, bogels2015}.

%Though children's anticipatory gazes did show some gains with age, adults on average still made more anticipatory switches than children in all conditions, even compared to 6-year-olds. Curiously, child and adult performance were much more similar by ages 3--5 in Experiment 1. This may indicate that children rely more in non-verbal cues in anticipating turn transitions or, alternatively, that adults are better at flexibly adapting to the turn-relevant cues present at any moment.

%Our results suggest that the question effect emerges between ages one and two, but further testing is needed to establish whether this is the case. For example, the size and emergence of the question effect for various question types and question cues could differ (\textit{wh-} vs. \textit{yes-no}; early vs. late in the utterance), but we do not have enough data to make those distinctions in the current analysis. Also, 43\% of one-year-olds already showed more switching for questions than non-questions in the \textit{normal} speech condition---the only condition with the full range of linguistic cues children hear in everyday life. Future work with more fine-grained age samples and better controlled \textit{normal} speech might then find that children can identify questions in conversation even earlier.

%We controlled linguistic information in Experiment 2 by using phonetically-manipulated speech, extending speech manipulations used in prior work \citep{de-ruiter2006, keitel2013}. While phonetic manipulation gave us control over the linguistic signal, it also created speech sounds that children don't usually hear in their natural environment. Many prior studies have used phonetically-altered speech with infants and young children \citep[cf.][]{jusczyk2000}, but almost none of them have done so in a conversational context. We found that the \textit{normal} speech condition showed the strongest anticipation effects over all, and we have attributed this to the fact that it gave participants full (lexicosyntactic and prosodic) linguistic information. However, it was also the only natural speech condition. Children could have had trouble processing the \textit{words only} and \textit{prosody only} conditions because they were unfamiliar, and not just because they had less linguistic information available.
%
%It would take a different type of stimulus to compare lexical and prosodic information without phonetic manipulation. For example, carefully scripted or cross-spliced conversations could control for the presence or absence of prosodic and lexicosyntactic cues to turn transition with natural speech. But since the non-natural (limited cue) linguistic conditions did still elicit some differences in anticipation, children must have processed at least some linguistic information in the \textit{prosody only} and \textit{words only} conditions. Perhaps the advantage of the \textit{normal} condition was then not entirely due to its naturalness. We expect that future work with spontaneous conversational measures will still find an advantage for combined lexical and prosodic cues over lexical cues alone \citep[see also][]{duncan1972, ford1996, torreira2015}.

%%%%%%%

%Children begin to develop conversational turn-taking skills long before their first words \citep{bateson1975, hilbrink2015, jaffe2001, snow1977}. As they acquire language, they also acquire the information needed to make accurate predictions about upcoming turn structure. Until recently, we have had very little data on how children weave language into their already-existing turn-taking behaviors. 
%
%In two experiments investigating children's anticipatory gaze to upcoming speakers, we found evidence that turn prediction develops early in childhood, and that linguistic cues are integrated differently at different ages. Children under three showed a general advantage for prosody over lexicosyntax, contrary to findings for adults in prior work \citep{de-ruiter2006}. Children two and older also showed a slight advantage for lexicosyntax, but only in the form of a transition type effect: They made more anticipatory switches following questions than non-questions in conditions where lexical information was present. Two-year-olds thus appeared to be at a developmental transition point, still showing an overall advantage for prosody, but beginning to show an advantage for lexicosyntax within the domain of question-answer sequences. We found no evidence that, for children or adults, lexicosyntax alone was ``sufficient'' (equal to full linguistic information) for spontaneous turn prediction \citep[pg. 531]{de-ruiter2006}: Participants' performance was best in conditions when they had access to the full linguistic signal. 
%
%\subsection{Developmental implications}
%
%The primary aim of our study was to find out how linguistic information affects children's predictions about upcoming turn structure across development. Two primary developmental findings emerged from our data. First, participants' spontaneous predictions largely occurred during question--answer transitions. Second, children's use of linguistic signals in making predictions depended on their age, with an early advantage for prosody over lexicosyntax and a later (partial) advantage for lexicosyntax over prosody.
%
%\subsubsection{The advantage for questions}
%
%In both of our experiments we found a robust advantage for questions in participants' anticipatory switching because participants made more switches after questions than non-questions. Children and adults both treated questions as if they had a special interactive status, and with good reason: Questions make a speaker switch immediately relevant, helping the listener to predict what will happen next (i.e., an answer from the addressee). Linguistic cues to questionhood often occur early in the utterance, making questions easy to identify early on and thereby giving observers time to plan a reaction (i.e., a gaze switch). Also, the form of a question can constrain the type of response that will come next (e.g., a location after a \textit{where} question), further increasing the predictability of the interactional sequence.
%
%Children get frequent and early experience with hearing and answering questions. Questions make up approximately one third of the utterances children hear, before and after the onset of speech, and even into their preschool years \citep{fitneva2012, henning2005, shatz1979}.\footnote{There is substantial variation in this proportion by individual and socioeconomic class \citep{hart1992}.} Many of the questions directed to young children are ``test' questions---questions that the caregiver already has the answer to (e.g., ``What does a cat say?''). Caregivers use questions to get their young children's attention and to ensure that information is in common ground, even if the responses are non-verbal or infelicitous \citep{bruner1985, fitneva2012, snow1977}. So, in addition to having a special interactive status, questions are a core characteristic of many caregiver-child interactions.
%
%We cannot definitively say with our current data what property of questions caused children to switch their gaze more often. It is true that questions make a speaker transition more likely and that questions have distinctive linguistic cues, both early and late, to identify themselves. But other speech acts and request formats have these same properties. Imperatives, compliments, and complaints all make a response from the addressee likely \citep{schegloff2007}. Rhetorical and tag questions, on the other hand, take a similar form to prototypical polar questions, but do not always require an answer. So, though it is clear that children anticipate responses more often for questions than non-questions, their actual understanding of questionhood as a linguistically- or interactionally-marked type of speech act still needs further exploration.
%
%\subsubsection{Linguistic cues for turn prediction}
%
%Prior work with adults has found a consistent and critical role for lexicosyntax in predicting upcoming turn structure \citep{de-ruiter2006, magyari2012}, with more debate over the role of prosody \citep{duncan1972, ford1996, torreira2015}. Knowing that children comprehend more about prosody than lexicosyntax early on (see introduction; also see \citealp{speer2009} for a review), we thought it possible that young children would instead show an advantage for prosody over lexicosyntax. Our results suggest that there are roles for both prosody and lexicosyntax in children's predictions about upcoming turn structure, but that there are different roles for these information sources at different ages.
%
%Early on, there was an advantage for prosody over lexicosyntax in children's anticipatory switches: Anticipatory switching didn't reliably exceed chance for lexicosyntactic information  until age three, but was already significantly greater than chance for prosodic information  at age one. This early advantage for prosody was not driven by the advantage for questions: While some one-year-olds in our study already made more switches after questions than non-questions, most did not, plus prosody alone did not elicit a robust question effect at any age (Figure \ref{fig:questionsEN}).
%
%Although children showed an initial advantage for prosody, their predictions before age three were probably limited to basic prosodic contours and boundaries, and simple cues such as final lengthening and turn-final silence \citep{pannekamp2006}. More complex structural predictions would have required them to access lexicosyntactic information because higher-level structure in the prosodic signal is linked to the syntactic structure being used.
%
%In both experiments, even young children showed an advantage for questions in conditions where they had lexicosyntax, suggesting that lexicosyntax is a critical cue for question identification. The question effect emerged by age two, when children's syntactic comprehension and lexical inventories are still relatively limited \citep{clark2009}. That being said, syntactic and lexical markers to questionhood in English are frequent, categorical, and early-occurring in the utterance (e.g., ``do'', \textit{wh}-words, and subject-auxiliary inversion). Lexicosyntactic question cues were available on every instance of \textit{wh}- and \textit{yes/no} questions in our stimuli, whereas prosodic question cues were only salient on \textit{yes/no} questions. Thus, the unambiguous presence of lexicosyntactic cues on \textit{wh}- and \textit{yes/no} questions may have been one reason why we saw an advantage for questions in the lexical conditions, but not in the \textit{prosody only} condition.
%
%Importantly, the question effect was not driven purely by lexicosyntactic information. In both experiments, prosody still made a contribution to the advantage for questions, even though prosody alone was not enough to elicit a question effect. For example, older children and adults in Experiment 1 showed a question effect in the languages they did not understand---presumably they used prosodic and non-verbal information to distinguish questions from non-questions. In Experiment 2, the advantage for questions was biggest for speech with lexicosyntactic \textit{and} prosodic information together. All in all, children appear to improve at identifying questions in ongoing conversation by using lexicosyntactic cues as they get older. But, prosodic cues still aid in picking out questions from ongoing conversation.
%
%The close link between prosodic and syntactic structure makes it difficult to tease apart how predictive processing in one domain (e.g., prosody) is distinct from the other (e.g., syntax) in turn prediction. We leave this challenge to future work.
%
%\subsection{Contributions of the current work}
%
%Our findings are consistent with observational work on children's turn taking. Young children are slow turn-takers in spontaneous conversation \citep{casillas2016} even though they begin taking turns in infancy \citep{hilbrink2015, jaffe2001}. We found that children begin to spontaneously predict upcoming turn structure at age one. Children's gaze switches were also most common in the inter-turn gap, suggesting that they expected an immediate response from the addressee. Our results therefore support the idea of an early-developed competence for the timing of turn taking. But because children do not themselves use adult-like conversational timing until much later \citep[age six; ][]{ervin-tripp1979}, our results also indirectly point toward response planning as a key factor contributing to children's slow responses in real-time interaction \citep{casillas2016}.
%
%Our findings are only partially consistent with prior experimental work on turn taking. De Ruiter and colleagues (2006) found that adults' accuracy in identifying upcoming turn-ends was not significantly affected when intonation contours were flattened. Keitel and colleagues (2013) found the same for adults' anticipatory gaze switches, only finding that intonation flattening affected children's switches at 36 months (with switches by younger children never exceeding chance). Our results, in contrast, suggest that children's anticipatory switches emerge much earlier, and rely on prosody before they do lexicosyntax. Furthermore, our adult control participants patterned similarly to the children: They showed question effects for languages they didn't speak (Experiment 1) and showed the strongest question effects for lexicosyntax and prosody together (Experiment 2). Thus, neither the child nor the adult data support the idea that lexicosyntactic information is equal to full linguistic information in making predictions about upcoming turn structure \citep{de-ruiter2006}, at least in participants' spontaneous looking behavior. This may partially be due to the fact that we controlled syllable duration in addition to intonation, thereby eliminating two of the most salient cues to prosodic structure. 
%
%Despite extreme differences in linguistic information across conditions, independent effects of linguistic information (outside of interactions) were minimal in our experiments. But, using a button-press measure with similar stimuli, de Ruiter and colleagues (2006) found robust effects of linguistic condition. This disparity in findings could be partially explained by task differences. A button-press method explicitly encourages participants to make an early response, while observer gaze measures are purely passive. Participants' spontaneous anticipatory gaze switches may not elicit enough early responses to see large linguistically-driven differences in prediction. Indeed, most switches happened during the inter-turn gap (Keitel et al., 2013; Hirvenkari, 2013; Tice and Henetz, \citeyear{TiceHenetz11}). Observers' gaze patterns suggest that they aren't targeting potential turn-ends with their predictions. Rather, they are targeting switches in speakership. So although button press measures may be better equipped to tell us what participants \textit{can} do in predicting turn ends, they may also emphasize early responding (and consequently, lexicosyntactic cues) to a greater extent than we experience in everyday conversation. Within observer gaze experiments, questions may be the key to naturally eliciting early responses. We have seen in the current study that questions are interactionally sufficient to motivate early predictions.
%
%Moving away from button press measures, Keitel and colleagues (2013) used observer gaze to investigate children's turn predictions, finding: (a) No evidence that children under three make switches above chance, (b) that three-year-olds' switches are significantly affected by flattened intonation, and (c) that adults' switches are not. Our current results are consistent with the general finding from their study, that prosody matters for young children's turn predictions. But our results also differ from theirs in a few important ways. 
%
%First, we found that children begin making above-chance anticipatory switches much earlier than three---our one-year-olds were already looking above chance in two of our four linguistic conditions in Experiment 2. This earlier emergence of anticipatory switching could be due to our more child-friendly stimuli, which we designed to be engaging and to mimic the kind of speech children often experience interactionally. Second, because we included more linguistic conditions to isolate the effects of prosody and lexicosyntax, we gained a broader perspective on how linguistic information changed children's predictions. Ultimately, the added conditions allowed us to find an early advantage for prosody and a later advantage for lexicosyntax.
%
%Third, we found that anticipatory looking was primarily driven by question transitions, a pattern that has so far not been discussed in other observer gaze studies, on children or adults (Keitel et al., 2013; Hirvenkari, 2013; Tice and Henetz, \citeyear{TiceHenetz11}). The question effects in the current study were critical to understanding the role of lexicosyntactic information in participants' turn predictions. Finally, we found that our adult controls were affected by the absence of prosody (within the question effect) while Keitel et al. (2013) found that adults' were unaffected by flattened pitch. But again, because we flattened pitch for individual speakers and controlled syllable duration, we are not able to directly compare our findings to theirs.
%
%\subsection{Limitations}
%
%In Experiment 2, we tried to improve our method for controlling linguistic information by phonetically manipulating improvised dialogic speech. Although this decision allowed us to follow prior work more closely \citep{de-ruiter2006, keitel2013}, it also limits our interpretation of children's behavior. Low-pass filtered and robotic-like speech are not typical within children's speech environment, and so it may have been unfair to compare the limited cue conditions in Experiment 2 to the normal speech condition, which not only had full linguistic cues, but is also more typically present in children's speech environments. One alternative to explore for the future would be scripted speech, cross-spliced speech, or speech that is carefully selected from a large corpus, given a set of specific linguistic constraints.
%

>>>>

\usepackage{graphicx}
% \usepackage{lineno}
\usepackage{amssymb}
\usepackage{wrapfig}
\usepackage{subfig}
\usepackage{tipa}
\usepackage{float}
\usepackage{longtable}

@@

@@

\begin{longtable}{lcccl}
  \textbf{\textit{Children}} &&&& \\
    \hline
                       & Estimate & Std. Error & z value & Pr($>$$|$z$|$)    \\
    \hline
    (Intercept)                & -3.57414  &   0.48576 &  -7.358 & 1.87e-13 ***    \\
    Age                         & 0.02543 &    0.10260  &  0.248   & 0.8042        \\
    Condition$=$\textit{muffled}         &   -1.63429  &   0.86390 &  -1.892   & 0.0585 .      \\
    Condition$=$\textit{normal}            &  0.36710 &    0.43296 &   0.848  &  0.3965        \\
    Condition$=$\textit{robot}            &  -0.26741 &    0.59071 &  -0.453  &  0.6508        \\
    Type$=$\textit{non-Question}                      & -0.81873  &   0.59985 &  -1.365  &  0.1723        \\
    Duration                   &  4.17672  &   0.62446  &  6.689 & 2.25e-11 ***    \\
    Age*Condition$=$\textit{muffled}       &   0.39317 &     0.18907 &   2.080  &  0.0376 *      \\
    Age*Condition$=$\textit{normal}       &   0.12919 &    0.10227  &  1.263  &  0.2065        \\
    Age*Condition$=$\textit{robot}           &   0.13740  &   0.13568   & 1.013  &  0.3112        \\
    Age*Type$=$\textit{non-Question}                &    0.15116   &  0.13643  &  1.108  &  0.2679        \\
    Condition$=$\textit{muffled}*     &  1.77190  &   1.24864  &  1.419 &   0.1559        \\
    Type$=$\textit{non-Question} &&&& \\
    Condition$=$\textit{normal}*     &   0.91059  &   0.72095  &  1.263 &   0.2066        \\
    Type$=$\textit{non-Question} &&&& \\
    Condition$=$\textit{robot}*     &   -1.02193  &   1.01227  & -1.010  &  0.3127        \\
    Type$=$\textit{non-Question} &&&& \\
    Age*Condition$=$\textit{muffled}* &  -0.47057 &    0.28703 &  -1.639 &   0.1011        \\
    Type$=$\textit{non-Question} &&&& \\
    Age*Condition$=$\textit{normal}* &   -0.37542  &   0.16963  & -2.213 &   0.0269 *      \\
    Type$=$\textit{non-Question} &&&& \\
    Age*Condition$=$\textit{robot}*  &   0.08946  &   0.22349   & 0.400 &   0.6890        \\
    Type$=$\textit{non-Question} &&&& \\
    \hline
  &&&& \\
  \textbf{\textit{Adults}} &&&& \\
    \hline
                       &  Estimate & Std. Error & z value & Pr($>$$|$z$|$) \\    
    \hline
    (Intercept)           &  -3.4557   &   0.7199 &  -4.800 & 1.58e-06 *** \\ 
    Condition$=$\textit{muffled}     &     0.3349  &    0.8965  &  0.374 & 0.708692     \\ 
    Condition$=$\textit{normal}    &      1.2556   &   0.5633  &  2.229 & 0.025805 *   \\ 
    Condition$=$\textit{robot}       &     1.5938  &    0.7208 &   2.211 & 0.027023 *   \\ 
    Type$=$\textit{non-Question}                  &   0.4292  &    0.6089  &  0.705 & 0.480916     \\ 
    Duration             &     4.7500   &   1.2480  &  3.806 & 0.000141 *** \\ 
    Condition$=$\textit{muffled}*  &  0.6627  &    1.2138 &   0.546 & 0.585108     \\ 
    Type$=$\textit{non-Question} &&&& \\
    Condition$=$\textit{normal}* &   -0.9452  &    0.7631 &  -1.239 & 0.215475     \\ 
    Type$=$\textit{non-Question} &&&& \\
    Condition$=$\textit{robot}*   &  -1.1265  &    0.9109  & -1.237 & 0.216201     \\ 
    Type$=$\textit{non-Question} &&&& \\
    \hline
  \caption{Model output for children and adults' anticipatory gaze switches.}
\label{tab:E2-models}
\end{longtable}

@@

Children begin to develop conversational turn-taking skills long before their first words \citep{bateson1975, hilbrink2015, jaffe2001, snow1977}. As they acquire language, they also acquire the information needed to make accurate predictions about upcoming turn structure. Until recently, we have had very little data on how children weave language into their already-existing turn-taking behaviors.

In two experiments investigating children's anticipatory gaze to upcoming speakers, we found evidence that turn prediction develops early in childhood and that spontaneous predictions are primarily driven by participants' expectation of an immediate response in the next turn. In making predictions about upcoming turn structure, children used a combination lexical and prosodic cues; neither prosodic nor lexical cues alone were sufficient to support increased anticipatory gaze. We also found no early advantage for prosody over lexicosyntax, and instead found that children were unable to make above-chance anticipatory gazes in the prosody only condition until age five. We discuss these findings with respect to the role of linguistic cues in predictions about upcoming turn structure, the importance of questions in spontaneous predictions about conversation, and children's developing competence as conversationalists.

\subsection{Predicting turn structure with linguistic cues}

Prior work with adults has found a consistent and critical role for lexicosyntax in predicting upcoming turn structure \citep{de-ruiter2006, magyari2012}, with the role of prosody still under debate \citep{duncan1972, ford1996, torreira2015}. Knowing that children comprehend more about prosody than lexicosyntax early on (see introduction; also see \citealp{speer2009} for a review), we thought it possible that young children would instead show an advantage for prosody over lexicosyntax. Our results suggest that, on the contrary, when presented with \textit{only} prosodic information, children's spontaneous predictions about upcoming turn structure are limited until age five. Do children instead rely on lexicosyntax, as adults are proposed to do?

We found no evidence that, for children, lexicosyntax alone is ``sufficient'' (equal to full linguistic information) for spontaneous turn prediction \citep[pg. 531]{de-ruiter2006}: In both experiments, children's performance was best in conditions when they had access to the full linguistic signal. Adults on the other hand, showed significant gains in anticipatory gaze switching in both conditions with lexical cues, compared to a no speech baseline.

Participants appeared to use linguistic cues to make more anticipatory gaze switches in both experiments. Questions are often marked both prosodically and lexicosyntactically for their speech act status. The close link between prosodic and syntactic structure makes it difficult to tease apart how predictive processing in one domain is distinct from the other in turn prediction. That being said, compared to prosodic contours (e.g., final rising intonation), lexicosyntactic cues like \textut{wh}-words, \textit{do}-insertion, and subject-auxiliary inversion are frequent, categorical, and early-occurring in the utterance. Children may therefore have an easier time picking out and interpreting lexical cues to questionhood on the fly. Question turns started yielding significantly more anticipatory gazes by age 3--4 in the normal speech condition of Experiment 2, by which time children frequently hear and use a variety of polar \textit{wh}-questions \citep{clark2009}. Furthermore, while lexicosyntactic question cues were available on every instance of \textit{wh}- and \textit{yes/no} questions in our stimuli, prosodic question cues were only salient on \textit{yes/no} questions and, even then, the mapping of prosodic contour to speech act (e.g., high final rises for polar questions) is far from one-to-one \citep{hedberg2010}.

Finally, we found that our adult controls were affected by the absence of prosody (within the question effect) while Keitel et al. (2013) found that adults' were unaffected by flattened pitch. But again, because we flattened pitch for individual speakers and controlled syllable duration, we are not able to directly compare our findings to theirs.

% WHAT CUES ARE THEY USING?

\subsubsection{The question effect}
% What exactly is the Q effect? Could it exist for non-Qs?
% When does the Q effect emerge and exactly what cues is it relying on?
% Are they predicting the form of the answer?

Third, we found that anticipatory looking was primarily driven by question transitions, a pattern that has so far not been discussed in other observer gaze studies, on children or adults (Keitel et al., 2013; Hirvenkari, 2013; Tice and Henetz, \citeyear{TiceHenetz11}). The question effects in the current study were critical to understanding the role of lexicosyntactic information in participants' turn predictions.

In both of our experiments we found a robust advantage for questions in participants' anticipatory switching because participants made more switches after questions than non-questions. Children and adults both treated questions as if they had a special interactive status, and with good reason: Questions make a speaker switch immediately relevant, helping the listener to predict what will happen next (i.e., an answer from the addressee). Linguistic cues to questionhood often occur early in the utterance, making questions easy to identify early on and thereby giving observers time to plan a reaction (i.e., a gaze switch). Also, the form of a question can constrain the type of response that will come next (e.g., a location after a \textit{where} question), further increasing the predictability of the interactional sequence.

Children get frequent and early experience with hearing and answering questions. Questions make up approximately one third of the utterances children hear, before and after the onset of speech, and even into their preschool years \citep{fitneva2012, henning2005, shatz1979}.\footnote{There is substantial variation in this proportion by individual and socioeconomic class \citep{hart1992}.} Many of the questions directed to young children are ``test' questions---questions that the caregiver already has the answer to (e.g., ``What does a cat say?''). Caregivers use questions to get their young children's attention and to ensure that information is in common ground, even if the responses are non-verbal or infelicitous \citep{bruner1985, fitneva2012, snow1977}. So, in addition to having a special interactive status, questions are a core characteristic of many caregiver-child interactions.

We cannot definitively say with our current data what property of questions caused children to switch their gaze more often. It is true that questions make a speaker transition more likely and that questions have distinctive linguistic cues, both early and late, to identify themselves. But other speech acts and request formats have these same properties. Imperatives, compliments, and complaints all make a response from the addressee likely \citep{schegloff2007}. Rhetorical and tag questions, on the other hand, take a similar form to prototypical polar questions, but do not always require an answer. So, though it is clear that children anticipate responses more often for questions than non-questions, their actual understanding of questionhood as a linguistically- or interactionally-marked type of speech act still needs further exploration.

Our results suggest that the question effect emerges between ages one and two, but further testing is needed to establish whether this is the case. For example, the size and emergence of the question effect for various question types and question cues could differ (\textit{wh-} vs. \textit{yes-no}; early vs. late in the utterance), but we do not have enough data to make those distinctions in the current analysis. Also, 43\% of one-year-olds already showed more switching for questions than non-questions in the \textit{normal} speech condition---the only condition with the full range of linguistic cues children hear in everyday life. Future work with more fine-grained age samples and better controlled \textit{normal} speech might then find that children can identify questions in conversation even earlier.

Because the form of an answer is partially determined by its question (e.g., locative expressions for ``where'' questions), participants could even be predicting what type of response they will hear, and so they are looking anticipatorily at the responder for confirmation of their prediction. This interpretation is initial, but in-line with work showing early response planning and speech act recognition \citep{gisladottir2015, bogels2015}.

\subsubsection{Early competence for turn taking?}
% When does children's performance become adult-like?

Though children's anticipatory gazes did show some gains with age, adults on average still made more anticipatory switches than children in all conditions, even compared to 6-year-olds. Curiously, child and adult performance were much more similar by ages 3--5 in Experiment 1. This may indicate that children rely more in non-verbal cues in anticipating turn transitions or, alternatively, that adults are better at flexibly adapting to the turn-relevant cues present at any moment.

First, we found that children begin making above-chance anticipatory switches much earlier than three---our one-year-olds were already looking above chance in two of our four linguistic conditions in Experiment 2. This earlier emergence of anticipatory switching could be due to our more child-friendly stimuli, which we designed to be engaging and to mimic the kind of speech children often experience interactionally. Second, because we included more linguistic conditions to isolate the effects of prosody and lexicosyntax, we gained a broader perspective on how linguistic information changed children's predictions. Ultimately, the added conditions allowed us to find an early advantage for prosody and a later advantage for lexicosyntax.

Our findings are consistent with observational work on children's turn taking. Young children are slow turn-takers in spontaneous conversation \citep{casillas2016} even though they begin taking turns in infancy \citep{hilbrink2015, jaffe2001}. We found that children begin to spontaneously predict upcoming turn structure at age one. Children's gaze switches were also most common in the inter-turn gap, suggesting that they expected an immediate response from the addressee. Our results therefore support the idea of an early-developed competence for the timing of turn taking. But because children do not themselves use adult-like conversational timing until much later \citep[age six; ][]{ervin-tripp1979}, our results also indirectly point toward response planning as a key factor contributing to children's slow responses in real-time interaction \citep{casillas2016}.

\subsection{Limitations}
% assumptions about saccadic planning time
% There is a problem with manipulated speech

We controlled linguistic information in Experiment 2 by using phonetically-manipulated speech, extending speech manipulations used in prior work \citep{de-ruiter2006, keitel2013}. While phonetic manipulation gave us control over the linguistic signal, it also created speech sounds that children don't usually hear in their natural environment. Many prior studies have used phonetically-altered speech with infants and young children \citep[cf.][]{jusczyk2000}, but almost none of them have done so in a conversational context. We found that the \textit{normal} speech condition showed the strongest anticipation effects over all, and we have attributed this to the fact that it gave participants full (lexicosyntactic and prosodic) linguistic information. However, it was also the only natural speech condition. Children could have had trouble processing the \textit{words only} and \textit{prosody only} conditions because they were unfamiliar, and not just because they had less linguistic information available.

It would take a different type of stimulus to compare lexical and prosodic information without phonetic manipulation. For example, carefully scripted or cross-spliced conversations could control for the presence or absence of prosodic and lexicosyntactic cues to turn transition with natural speech. But since the non-natural (limited cue) linguistic conditions did still elicit some differences in anticipation, children must have processed at least some linguistic information in the \textit{prosody only} and \textit{words only} conditions. Perhaps the advantage of the \textit{normal} condition was then not entirely due to its naturalness. We expect that future work with spontaneous conversational measures will still find an advantage for combined lexical and prosodic cues over lexical cues alone \citep[see also][]{duncan1972, ford1996, torreira2015}.

In Experiment 2, we tried to improve our method for controlling linguistic information by phonetically manipulating improvised dialogic speech. Although this decision allowed us to follow prior work more closely \citep{de-ruiter2006, keitel2013}, it also limits our interpretation of children's behavior. Low-pass filtered and robotic-like speech are not typical within children's speech environment, and so it may have been unfair to compare the limited cue conditions in Experiment 2 to the normal speech condition, which not only had full linguistic cues, but is also more typically present in children's speech environments. One alternative to explore for the future would be scripted speech, cross-spliced speech, or speech that is carefully selected from a large corpus, given a set of specific linguistic constraints.

Relatedly, since we used improvised conversation recordings, we did not control how often the speakers switched back and forth, or how often a switch occurred after a pause in speech. It is possible that, to some extent, children could have formed expectations about the turn structure on the basis of the frequent switching alone \citep[see, e.g., ][]{thorgrimsson2015}. If this statistical expectation were the only thing leading children's anticipatory gaze switches, we would have predicted more uniformity in looking behavior across the conditions and no major effects of linguistic signal, age, or transition type. But that is not what we saw. Nevertheless, another advantage of using scripted conversation would be the ability to control switch frequency and eliminate this issue.

Finally, we carefully designed a scheme for identifying anticipatory turn switches in the data, building off of Keitel and colleagues' (2013) analyses. In both our study and theirs, anticipatory switches that happen very early in the turn are not counted. Instead, they would actually count as ``random'' switches in the baseline analyses. These same early switches are counted as non-random in other studies of children's gaze to conversational stimuli \citep{bakker2011, hofsten2009}. Since most studies, even those using a wider switching window \citep[e.g., ][]{hirvenkari2013} find that switches primarily happen close to or immediately after the inter-turn gap begins, the approach used here and in Keitel et al. (2013) probably captures most of participants' turn-relevant switching behavior. But if early looks do indeed increase as children get older and have more access to early syntactic cues, it would be helpful to develop a second measure of very early anticipatory looks.

Despite extreme differences in linguistic information across conditions, independent effects of linguistic information (outside of interactions) were minimal in our experiments. But, using a button-press measure with similar stimuli, de Ruiter and colleagues (2006) found robust effects of linguistic condition. This disparity in findings could be partially explained by task differences. A button-press method explicitly encourages participants to make an early response, while observer gaze measures are purely passive. Participants' spontaneous anticipatory gaze switches may not elicit enough early responses to see large linguistically-driven differences in prediction. Indeed, most switches happened during the inter-turn gap (Keitel et al., 2013; Hirvenkari, 2013; Tice and Henetz, \citeyear{TiceHenetz11}). Observers' gaze patterns suggest that they aren't targeting potential turn-ends with their predictions. Rather, they are targeting switches in speakership. So although button press measures may be better equipped to tell us what participants \textit{can} do in predicting turn ends, they may also emphasize early responding (and consequently, lexicosyntactic cues) to a greater extent than we experience in everyday conversation. Within observer gaze experiments, questions may be the key to naturally eliciting early responses. We have seen in the current study that questions are interactionally sufficient to motivate early predictions.

\subsection{Conclusions}
%
%Conversation plays a central role in children's language learning. It is the driving force behind what children say and what they hear. And yet many conversational skills, like turn taking, rely heavily on language. Adults use language to accurately predict turn structure in conversation, which facilitates their online comprehension and allows them to respond relevantly and on time. But young children do not have enough linguistic knowledge to take turns the way that adults do. Instead, they first acquire a preverbal turn-taking system for interaction, and then somehow assimilate language into that system as they acquire it. The simultaneous acquisition and integration of interactive and linguistic skills is no easy task, as evidenced by children's protracted development of turn-taking skills. In the current study we have investigated children's language acquisition through the lens of turn taking, thereby bringing into focus children's application of linguistic knowledge in real-time interaction. We found that children acquire basic predictive skills early on, but that the integration of linguistic cues takes time and is primarily driven by sequences of action---in our case, by questions and their answers.
